### 2020-05-11 README.Rmd
small changes to rEADME

```{r, include = FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

```{r, eval = FALSE}
devtools::install_github("https://github.com/AIMS/data-platform-r")
```

>>>>

```{r, include = FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

@@

```{r, eval = FALSE}
devtools::install_github("https://github.com/AIMS/dataaimsr")
```
